For a Systematic Sensitivity Analysis of Spatial Meta-parameters in Models of Simulation

### 2017-04-03 paper.tex
Update on Overleaf.

@@

%%%%%%%%%%%%%%%
\begin{figure}
\centering
%
\caption{Meta phase diagram, i.e. phase diagram of phase diagram behavior, along parameters of spatial configuration generation ($\alpha$,$n_D$,$\beta$,$N_G$) \todo{described these somewhere}, aggregated for each as an Earth Mover Distance to a fixed reference (phase diagram of Fig.~\ref{fig:sugarscape-phasediagram}).}
\label{fig:sugarscape-meta}
\end{figure}
%%%%%%%%%%%%%%%

>>>>

\usepackage{graphicx}

@@

%%%%%%%%%%%%%%%
\begin{figure}
\centering
%
\caption{Meta phase diagram, i.e. phase diagram of phase diagram behavior, along parameters of spatial configuration generation ($\alpha$,$n_D$,$\beta$,$N_G$) (described these somewhere), aggregated for each as an Earth Mover Distance to a fixed reference (phase diagram of Fig.~\ref{fig:sugarscape-phasediagram}).}
\label{fig:sugarscape-meta}
\end{figure}
%%%%%%%%%%%%%%%
